\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2020-12-23 manuscript.Rnw
First draft of conculsion

%% -- Conclusion ---------------------------------------------------------------
\section{Conclusion} \label{sec:conclusion}

>>>>

%% -- Conclusion ---------------------------------------------------------------
\section{Conclusion} \label{sec:conclusion}
\pkg{hesim} is a modular and computationally efficient \proglang{R} package for development and analysis of simulation models for economic evaluation. Discrete-time cohort and continuous-time individual-level models are supported, encompassing Markov (time-homogeneous and time-inhomogeneous) and semi-Markov processes as well as partitioned survival analysis. To facilitate integration of statistical methods and economic models and use of both patient- and aggregate-level data, parameters can be estimated by fitting a statistical model with \proglang{R}, inputting parameter estimates from an external source, or a combination of the two. Simulated costs and QALYs from a PSA can be used for for decision-analysis within a cost-effectiveness framework, allowing users to represent decision uncertainty (e.g., cost-effectiveness planes, cost-effectiveness acceptability curves, and cost-effectiveness acceptability frontiers), and conduct value of information analysis. Algorithms are efficiently coded and written in \proglang{C++} so that approaches that have been considered computationally intensive such as individual-level simulations and PSA can run very quickly. The modular design makes modeling more flexible and makes it straightforward to add new features.
